%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cvexperience
    {Data-drive analysis of heavy quark transport coefficients in heavy-ion collisions.} % Job title
    {Graduate Research: } % Organization
    {Duke University} % Location
    {Jan 2016 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Utilized the Bayesian model-to-data analysis, extracted the heavy quark transport coefficient in QGP medium.}
      	\item {Described the experimental measurements of $D$-meson observables in both RHIC and LHC energies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvexperience
    {Heavy flavor dynamics in proton-nucleus collisions.} % Job title
    {Graduate Research: } % Organization
    {Duke University} % Location
    {Aug 2013 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Established a comprehensive framework to simulate the full space-time evolution of heavy quarks in a QGP medium.}
      	\item {Quantified the medium modification of heavy quarks ans collective behaviors of small systems.}
      \end{cvitems}
    } 
    

%---------------------------------------------------------
  \cvexperience
    {A theoretical study on transport properties of electrons in an infinite carbon nanotubes.} % Job title
    {Undergrad Research: } % Organization
    {Nanjing University} % Location
    {Oct 2012 - Jun 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Applied Laudau formalism and Green's function to calculate the transport properties of electrons in idea nanotubes.}
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry
    {Teaching assistant} % Job title
    {Teaching Experience: } % Organization
    {Duke University} % Location
    {Aug 2013 - May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {grad-level statistical mechanics and quantum mechanics.}
      	\item {undergrad introduction to mechanics and introduction to astronomy.}
      \end{cvitems}
    } 

%---------------------------------------------------------
\end{cventries}
