%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\begin{enumerate}[wide, labelwidth=!, labelindent=0pt]
%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Talk:} Open heavy flavor transport models} % Role
    {RHIC \& AGS Annual User Meeting 2018} % Event
    {BNL, USA} % Location
    {June. 2018} % Date(s)

%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Poster:} Data-drive analysis of the temperature and momentum dependence of the charm quark diffusion coefficient} % Role
    {Quark Matter 2018} % Event
    {Venice, Italy} % Location
    {May. 2018} % Date(s)

%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Talk:} Data-drive analysis of the temperature and momentum dependence of the charm quark diffusion coefficient} % Role
    {Heavy Flavor Workshop in High Energy Collisions} % Event
    {LBNL, USA} % Location
    {Nov. 2017} % Date(s)

%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Mini-symposium:} Bayesian extraction of the heavy quark diffusion coefficient from RHIC and LHC heavy-ion data} % Role
    {Fall Meeting of the APS Division of Nuclear Physics} % Event
    {Pittsburgh, USA} % Location
    {Oct. 2017} % Date(s)

%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Parallel Talk:} Bayesian application on heavy quarks} % Role
    {Strangeness in Quark Matter} % Event
    {Utrecht, Netherlands} % Location
    {Jul. 2017} % Date(s)




%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Parallel Talk:} Data-drive analysis of the heavy quark transport coefficients} % Role
    {Quark Matter 2017} % Event
    {Chicago, USA} % Location
    {Feb. 2017} % Date(s)




%---------------------------------------------------------
\item 
  \cvsubsubentry
    {\entrypositionstyle{Parallel Talk:} Data-drive analysis of the temperature and momentum dependence of the heavy quark transport coefficients} % Role
    {Hard Probe 2016} % Event
    {Wuhan, China} % Location
    {Sep. 2016} % Date(s)



    
%---------------------------------------------------------
  \item 
  \cvsubsubentry
    {\entrypositionstyle{Parallel Talk:} Heavy flavor dynamics in proton-nucleus collisions} % Role
    {Hard Probe 2015} % Event
    {Montreal, Canada} % Location
    {Jul. 2015} % Date(s)


\end{enumerate}














%---------------------------------------------------------
\end{cventries}
